An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-14 paper/paper.tex
Fix compile error and comment out random thoughts/notes

  \textit{metadata record}

The metadata layer is used for three purposes:

\begin{

In this sense, the metadata layer can be thought of as the bookkeeper for our system.

  It serves three functions: (1) peers uses it to find holds information meta-information about each backup that occurs, along with additional information needed for the node selection process. Figure \ref{fig:metadata} enumerates the information stored in the metadata layer.

>>>>

%  \textit{metadata record}

%The metadata layer is used for three purposes:

%In this sense, the metadata layer can be thought of as the bookkeeper for our system.

%  It serves three functions: (1) peers uses it to find holds information meta-information about each backup that occurs, along with additional information needed for the node selection process. Figure \ref{fig:metadata} enumerates the information stored in the metadata layer.
